Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-05 Report06-12.Rmd
Plot changes

```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}"}
library(ggmosaic)
#dev tools version has scale_y_productlist but cannot use it yet
#aminFaces$shotangle 
aminFaces$shotangle <- factor(aminFaces$shotangle, levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))

MosaicShotangle<- ggplot(data=aminFaces) + 
  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
  #geom_text(aes(label="test", x=1, y=0.6)) +
  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
  labs(caption="") + coord_flip() +
  ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none") +
  ggtitle("Plot a. Proportion of faces captured at each angle")
```

@@

MosaicSit<- ggplot(data=aminFaces) + 
  geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
  labs(caption="") + coord_flip() +
  ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")  +
  ggtitle("Plot b. Proportion of faces captured in each situation")
```

@@

sbbgshot <- ggplot(data=aminFaces) +
   geom_bar(aes(x=shotangle, fill = bg), 
            position = position_stack(reverse = TRUE), 
            na.rm=TRUE) +
  coord_flip() +
  guides(fill = guide_legend(title="Background")) +
  labs(caption="") +
  ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none") +
  ggtitle("Plot c. Proportion of faces captured at each angle \nwith various backgrounds")

@@

sbbgsit <- ggplot(data=aminFaces) +
   geom_bar(aes(x=situation, fill = bg), 
            position = position_stack(reverse = TRUE), 
            na.rm=TRUE) +
  coord_flip() +
  guides(fill = guide_legend(title="Background")) +
  labs(caption="") +
  ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none") +
  ggtitle("Plot d. Proportion of faces captured in each situation \nwith various backgrounds")
```

@@

```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "These plots indicate the proportion or amount of faces with certain attributes, or attribute combinations.\\label{fig:ICFigs}"}

grid.arrange(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
             nrow=2, ncol=2)
```

@@

## Miscellaneous

#### Challenges
It is understandable that there would be many more faces to recognize in these shots than in shots where there is only a player, and therefore many more faces recognized. This provides many faces to sort through to find emotions of a player.

We faced the challenge of accessing usable images of players, and specifically their faces.
- Availability of software
- Using the software
- Time constraints

Method, automated the process to reduce data cleaning and help group characteristics

Pricing

Employ the Google Vision API, which would allow the use of still images, or video (TEST VIDEO) files, reducing the need for stills.
This product - cost in relation
Ease of access - API calling

>>>>

```{r MosaicShotangle, fig.cap = "\\label{fig:Mosaic}"}
aminFaces$shotangle <- factor(aminFaces$shotangle, 
                              levels = c("Birds Eye","Upward Angle","Player Shoulder Height"))

MosaicShotangle <- ggplot(data=aminFaces) + 
  geom_mosaic(aes(x=product(shotangle), fill=matchesManual)) +
  #geom_text(aes(label="test", x=1, y=0.6)) +
  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
  labs(caption="") + 
  scale_x_productlist(labels=c("Birds Eye"="Birds \nEye",
                            "Upward Angle"="Upward \nAngle",
                            "Player Shoulder Height" =
                            "Player \nShoulder \nHeight")) + coord_flip() +
  ylab("Proportion of faces") + xlab("Angle the face was captured from ") + theme(legend.position = "none") +
  ggtitle("Plot a. Proportion of faces captured \nat each angle") 
```

@@

MosaicSit<- ggplot(data=aminFaces) + 
  geom_mosaic(aes(x=product(situation), fill=matchesManual)) +
  guides(fill = guide_legend(title="API faces match \nmanual faces"))  +
  labs(caption="") + 
  scale_x_productlist(labels=c("Court close−up not player"="Court \nclose−up \nnot player",
          "Court in play"="Court \nin play",
          "Off court close up of player"="Off court \nclose up \nof player",
          "Crowd"="Crowd",
          "Court player close−up"="Court \nplayer \nclose−up")) +
  coord_flip() +
  ylab("Proportion of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none")  +
  ggtitle("Plot b. Proportion of faces captured \nin each situation")
```

@@

sbbgshot <- ggplot(data=aminFaces) +
   geom_bar(aes(x=shotangle, fill = bg), 
            position = position_stack(reverse = TRUE), 
            na.rm=TRUE) + 
  scale_x_discrete(labels=c("Birds Eye"="Birds \nEye",
                            "Upward Angle"="Upward \nAngle",
                            "Player Shoulder Height" =
                            "Player \nShoulder \nHeight"))+
  coord_flip() +
  guides(fill = guide_legend(title="Background")) +
  labs(caption="") +
  ylab("Amount of faces") + xlab("Angle the face was captured from") + theme(legend.position = "none") +
  ggtitle("Plot c. Proportion of faces captured\nat with each background given the angle")

@@

sbbgsit <- ggplot(data=aminFaces) +
   geom_bar(aes(x=situation, fill = bg), 
            position = position_stack(reverse = TRUE), 
            na.rm=TRUE) +
  scale_x_discrete(labels=c("Court close−up not player"="Court \nclose−up \nnot player",
          "Court in play"="Court \nin play",
          "Off court close up of player"="Off court \nclose up \nof player",
          "Crowd"="Crowd",
          "Court player close−up"="Court \nplayer \nclose−up")) +
  coord_flip() +
  guides(fill = guide_legend(title="Background")) +
  labs(caption="") +
  ylab("Amount of faces") + xlab("Situation the face was captured during") + theme(legend.position = "none") +
  ggtitle("Plot d. Proportion of faces captured\n with each background given the situation")
```

@@

```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually. The stacked bar charts show the amount of faces captured at certain angles, or situation, .\\label{fig:ICFigs}"}

plots <- arrangeGrob(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
             nrow=2, ncol=2)

g <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
lheight <- sum(legend$height)

grid.arrange(plots, legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight))
```

@@

```{r glasses, fig.cap = "This cross table compares the amounts and percentages of faces captured and whether the person was wearing glasses. The first row is the faces that were tagged as not wearing glasses, the second row is faces that were. For the API to not have been affected by the prescence of glasses, the proportion should be similar to that found manually. Animetrics had the highest proportio difference, 93.31% of the faces it found did not have glasses. Google is the closest proportion, 88.62% of the faces it found were wearing glasses.\\label{tab:glasses}"}

aminFaces %>%
  #filter(type=="Manual" | type=="Google") %>%
  droplevels(.) %>%
  CrossTable(data=., table(.$glasses, .$type), 
               prop.chisq = FALSE, 
               digits=2,
               expected = FALSE,
           prop.r = FALSE, prop.c = TRUE, prop.t = FALSE,
           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
           dnn = c("Glasses","Headwear")) -> mgct

pander(mgct, caption = "")
```
